The paper on \Large \bf Blockchain Frontrunning

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] reconstruct the mitigation methods

\subsection{How are Blockchain Applications Vulnarable to Front-running?}
\label{sec:Front Running on the Blockchains}

@@

\section{How to stop front-running?}
In the traditional markets, front-running is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain orderbooks. The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
%@shayan: ^

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run-resistent , and the other to design the application logics in a way that front running is not possible.

\subsection{front-run-resistent Blockchain}
What does this mean to have a front-run-resistent blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).

\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.

\begin{itemize}
\item{\textbf{Privacy Preserving Blockchians}: Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned. Although this limites the functionality of the blockchain/smartcontracts/dapps }
\item{textbf{Loopring/Dual Athoring}: Talk about this possible solution}

\end{itemize}

@@

\begin{itemize}
\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc}) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}. Commitment scheme is a good method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

@@

%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
\item{\textbf{Submarine Commitments}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

\item{\textbf{Application logic specific solution}: Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so. As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions. 
Another example for decentral orderbook design could be using call market design instead of  time-sensitive orderbooks. In such design the arrival time of the order does not matter as they are executed in batches. }
% talk about Incentivized mitigation method designs to prevent front running.

@@

\end{itemize}

>>>>

\subsection{How are Blockchain Applications Vulnerable to Front-running?}
\label{sec:Front Running on the Blockchains}

@@

\section{How to stop Front-running?}
In the traditional markets, front-running is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain orderbooks. The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
%@shayan: ^

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.

\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases).

\subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}

One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.

\subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}
Shielded transactions in ZCash do not reveal the sender, receiver, the amount and the data included in the transactions, hence they cannot be seen by network participants to be front-runned. Although this limits the functionality of the blockchain/smartcontracts/dapps

\subsubsection{Design Decision \#3: Loopring/Dual Authoring\newline}
Talk about this possible solution

%TODO: research on more proposed solutions!

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline}
Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}. Commitment scheme is a good method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

@@

%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
\subsubsection{Design Decision \#2: Submarine Commitments\newline}
describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.

\subsubsection{Design Decision \#3: Logic Specific Solution\newline}
Depending on the use case of  the Dapp or the application, it could be designed in a way to deincentives some actors to front-run the transactions or prevent them from doing so. As an example on desiging a decentral orderbook, it could be said that a miner could front run orders for financial gain on price improvement, however if the fees of the orders are sent to the miner of the block, it deincentiveses the miner to front run the orders as they already gain enough financial benefit from including the correct order of transactions. 
Another example for decentral orderbook design could be using call market design instead of  time-sensitive orderbooks. In such design the arrival time of the order does not matter as they are executed in batches. 
% talk about Incentivized mitigation method designs to prevent front running.

@@

%TODO: research on more possible solutions!
